The Perfect Bathtub Experience

### 2016-02-01 article/nontech.tex
more nontech

	For those of you whom like to include bubble bath in your bathtub, you're in luck: bubble bath aids water's heat retention abilities by providing more outlets for water to push its heat towards. In the short term, you will have less issues maintaining your warm bubble bath for a longer period of time. In the long term however, you will need to resort to trickling water into the bathtub to maintain heat just like if you were not using bubble bath at all.

	And there it is folks! The perfect bath secrets exposed.

>>>>

	Another helpful tactic to maintaining your bathtub temperature is to keep the water constantly in motion. You can help this process by moving around in the bathtub to move the warm water from the faucet to the outer reaches of the bathtub not near the faucet. This tactic helps because warm water from the faucet diffuses its heat to the surrounding cooler water molecules. When colder water molecules are surrounded by warmer water molecules, the bathtub water will heat up faster.

	And there it is folks! The perfect bath secrets exposed. To reiterate, the optimal strategy is to maintain a constant input of warm water from the faucet and to assist the warm water flow from to the various sides of the bathtub.
